TRIK Studio: Technical Introduction

### 2017-03-09 2017-trikStudioEnglish/trikStudioEnglish.tex
Added some not-so-convincing remarks answering reviewer concerns

Current paper describes TRIK Studio programming environment, which attempts to solve the aforementioned problems. TRIK Studio is widely used in Russian education organizations (almost a hundred of schools and robotic clubs), several applications in Great Britain, France and Singapore are known. This paper presents technical overview of the programming environment; educational and methodical issues are not discussed in detail.

@@

Technical description of the TRIK Studio robots programming system was presented. TRIK Studio now has about ten thousand users across the globe, according to Google Analytics data. Now it supports English, Russian and French languages. It is open source\footnote{https://github.com/qreal/qreal (accessed: 07.02.2017)} and has large and active community developing it. TRIK Studio has about 100K lines of code (excluding QReal core, which also has size of about 120K LOC), written in C++ with Qt.

>>>>

Current paper describes TRIK Studio programming environment, which attempts to solve the aforementioned problems. TRIK Studio is widely used in Russian education organizations (almost a hundred of schools and robotic clubs), several applications in Great Britain, France and Singapore are known. This paper presents technical overview of the programming environment; educational and methodical issues are not discussed in detail. Main scientific contribution of this article is a case study --- it describes an experience of creating robot programming environment specifically for school education and proposes ideas about language design and features which can be implemented in other such systems. It can also be viewed as an evidence of feasibility of using general-purpose domain-specific visual modeling platform to create domain-specific solution for wide audience.

@@

Technical description of the TRIK Studio robots programming system was presented. TRIK Studio now has about ten thousand users across the globe, according to Google Analytics data. Now it supports English, Russian and French languages. It is open source\footnote{https://github.com/qreal/qreal (accessed: 07.02.2017)} and has large and active community developing it. TRIK Studio has about 100K lines of code (excluding QReal core, which also has size of about 120K LOC), written in C++ with Qt. Good reception of TRIK Studio in educational robotics community may be viewed as a proof that modeling environment created with domain-specific platform (QReal in this case) can actually compete with visual programming environments written specifically for robots programming.
